Amen to replication: What have we learned about networks in International relations 

### 2016-11-25 amenIntro/amenIntro.Rmd
timeline updates

* Any missingness in covariates inputted into AME automatically get turned into 0 ... this is not good.
* We can get around this via imputing nodal and dyadic variables within AME
	- In this vein, I made a modified version of sbgcop that works over nodal and dyadic data...but we still need to incorporate this within the AME MCMC
	- also *within* because otherwise we'd have to run each model k times over different imputed datasets and use Rubin's rules to combine parameter estimates ... problematic especially when it comes to third order deps
* Computation time ... these models take a notable amount of time to converge
	- Mike's tower?
	- EC2 ... though the costs can build

@@

* Teams of two, each of you will be paired with someone experienced in AME
	- Dorff + Foster
	- Gallop + Liu
	- Ward + Roberts
	- Me + Tellez 
* Claim the replications you want to do on Google sheets ... whoever gets there first wins.
	- Mansfield + Milner is already mine.
* <span style="color:red">**How many replications should we do?**</span>
	- I propose two.
* <span style="color:red">**Timeline?**</span>
	- AT LEAST ONE REPLICATION MODEL RUNNING BY JANUARY 1
	- Paper draft end of January
* <span style="color:red">**What else?**</span>

>>>>

* Any missingness in covariates inputted into AME automatically get turned into 0 ... this is not good.
* We can get around this via imputing nodal and dyadic variables within AME
	- In this vein, I made a modified version of sbgcop that works over nodal and dyadic data...but we still need to incorporate this within the AME MCMC
	- also *within* because otherwise we'd have to run each model k times over different imputed datasets and use Rubin's rules to combine parameter estimates ... problematic especially when it comes to third order deps
* <span style="color:red">**Computation time**</span> ... these models take a notable amount of time to converge
	- Mike's tower?
	- EC2 ... though the costs can build

* Teams of two, each of you will be paired with someone experienced in AME
	- Dorff + Foster
	- Gallop + Liu
	- Ward + Roberts
	- Me + Tellez 
* Claim the replications you want to do on Google sheets ... whoever gets there first wins.
* <span style="color:red">**How many replications should we do?**</span>
	- I propose two per team.
* <span style="color:red">**Timeline**</span>
	- Decide on your two replication pieces by December 1
	- EACH TEAM SHOULD HAVE AT LEAST ONE REPLICATION MODEL RUNNING BY JANUARY 1
	- Paper draft end of January
* <span style="color:red">**What else?**</span>

@@
